%-------------------------
% Resume in Latex
% Author : Ulmasbek Rakhmatullaev
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}%[hidelinks]
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\bluebox}[1]{\fcolorbox{white}{white}{#1}}

\definecolor{linkcolor}{RGB}{0,0,255}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{{\Large Ulmasbek Rakhmatullaev}} & Email: \bluebox{\href{mailto:rakhmatullaevulmas@gmail.com}{rakhmatullaevulmas@gmail.com}} \\ 
    \textbf{Senior Flutter Developer} & Mobile: \bluebox{\href{tel:+998917940244}{+998 91 794 02 44}} \\
    Linkedin: \bluebox{\href{https://linkedin.com/in/ulmasbek}{linkedin.com/in/ulmasbek}} Github: \bluebox{\href{https://github.com/sudo-ulmas}{github.com/sudo-ulmas}} & Telegram: \bluebox{\href{https://t.me/abdullah_rkhm}{abdullah\_rkhm}}
\end{tabular*}

\vspace{-10pt}

%----------SUMMARY-----------------
\section{Professional Summary}
\small{Senior Flutter Developer with 5+ years of experience architecting cross-platform mobile solutions and leading development teams. Specialized in building SDKs, implementing platform-level integrations, and optimizing app performance. Proven track record in fintech, e-commerce, and enterprise applications. Strong foundation in mobile architecture, CI/CD automation, and mentoring engineering teams. Expanding expertise into backend development with Python/Django.}

\vspace{-5pt}

% --------PROGRAMMING SKILLS------------
\section{Technical Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Mobile Development:} Flutter, Dart, Swift, UIKit, Android, Platform Channels, Flutter Modules (Add-to-App)
     \vspace{-8pt}
   }
   \item{
     \textbf{State Management \& Architecture:} Bloc/Cubit, Provider, GetX, Clean Architecture, SOLID Principles
     \vspace{-8pt}
   }
   \item{
     \textbf{Testing \& Quality:} Unit Testing, Widget Testing, TDD, Firebase Test Lab, Crashlytics, Sentry
     \vspace{-8pt}
   }
   \item{
     \textbf{DevOps \& Tools:} CI/CD, Fastlane, GitLab, Git, Performance Optimization, DevTools
     \vspace{-8pt}
   }
   \item{
     \textbf{Backend \& Integration:} Python, Django (learning), REST APIs, SSO, Passkeys, Biometric Authentication
     \vspace{-8pt}
   }
   \item{
     \textbf{Methodologies:} Scrum, Kanban, Jira, Confluence, Code Reviews, Team Leadership
     \vspace{-8pt}
   }
   \item{
     \textbf{Languages:} English (Fluent), Russian (Fluent), Uzbek (Native)
   }
 \resumeSubHeadingListEnd

\vspace{-5pt}

%-----------EXPERIENCE-----------------
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Payfintech (Pully Platform)}{Tashkent, Uzbekistan}
      {Senior Flutter Developer}{January 2024 - Present}
      \resumeItemListStart
        \resumeItem{Architected and built cross-platform authentication SDK from scratch for the Pully platform, serving 4 major banks (Agrobank, Open Bank, MKB, BRB) with 150K+ monthly active users across mobile and web.}
        \resumeItem{Sole Flutter engineer responsible for SDK development, delivering native iOS/Android integration via Flutter Add-to-App and web integration via Flutter Web, enabling seamless authentication across all platforms.}
        \resumeItem{Implemented advanced authentication features including Passkeys integration, MyID biometric verification, and secure token-based authentication flow, reducing user login friction by 40\%.}
        \resumeItem{Designed SDK architecture to be modular and extensible, enabling rapid integration for new banking partners with minimal configuration.}
      \resumeItemListEnd

    \resumeSubheading
      {Eriell}{Tashkent, Uzbekistan}
      {Senior Flutter Developer}{May 2023 - January 2024}
      \resumeItemListStart
        \resumeItem{Built specialized Android-based warehouse management applications for manufacturing facilities, integrating barcode scanners, thermal printers, and custom hardware via Platform Channels.}
        \resumeItem{Engineered CI/CD pipelines with Fastlane and GitLab, reducing deployment cycle time significantly.}
        \resumeItem{Significantly reduced app crash rates and ANRs by implementing comprehensive observability stack with Firebase Crashlytics and Sentry, achieving 99.5\% crash-free sessions.}
        \resumeItem{Maintained and refactored legacy codebases, improving code quality and reducing technical debt.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Vention}{Wroclaw, Poland}
      {Middle Flutter Developer}{January 2022 - April 2023}
      \resumeItemListStart
        \resumeItem{Built internal employee platform with SSO authentication integrated across Vention's prouduct ecosystem.}
        \resumeItem{Actively participated in agile ceremonies, daily standups, sprint planning, retrospectives, and SP estimations.}
        \resumeItem{Conducted code reviews, 2 PR's/day, ensuring code quality, adherence to best practices, and knowledge sharing.}
      \resumeItemListEnd

    \resumeSubheading
      {UIC Group}{Tashkent, Uzbekistan}
      {Flutter Developer / Team Lead}{May 2020 - January 2022}
      \resumeItemListStart
        \resumeItem{Led a team of 8 Flutter developers, successfully delivering 13 production applications across diverse industries including e-commerce, news media, education, school management, insurance, and social networking.}
        \resumeItem{Mentored and onboarded 5+ junior developers, establishing Flutter best practices, coding standards and building internal knowledge base that became company-wide guidelines.}
        \resumeItem{Optimized resource allocation and project workflows, increasing team capacity by 40\% and enabling the company to take on larger client engagements.}
        \resumeItem{Integrated native Java/Kotlin modules into Flutter applications using Platform Channels, enabling access to Android-specific hardware and SDKs.}
        \resumeItem{Collaborated with cross-functional teams (Design, QA, Backend, DevOps, PM) during all project phases from ideation to production deployment.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\vspace{-5pt}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Inha University}{Tashkent, Uzbekistan}
      {Bachelor of Science in Computer Science;  GPA: 3.60}{August 2016 - May 2020}
  \resumeSubHeadingListEnd

\vspace{-10pt}

%-------------------------------------------
\end{document}
